Unreliable heterogeneity: how measurement error obscures heterogeneity in meta-analyses in psychology

### 2023-06-18 manuscript/manuscript.qmd
fix flowchart + descriptive text

## Meta-analytic modelmet0000498

@@

```{r Figure 1, out.width= "85%"}
#| fig.env: figure*
#| fig-pos: 't'
#| fig-cap: "Figure 1. Flowchart summarizing the simulation design."

>>>>

## Meta-analytic model

@@

```{r Figure 1, out.width= "90%"}
#| fig.env: figure*
#| fig-pos: 't'
#| fig-cap: "Flowchart summarizing the simulation design. For product-moment correlations, option (1) corresponds to the Hedges and Vevea (1998) model and option (2) to the Schmidt and Hunter (2015) model (see methods section 'Meta-analytic model'). $\\theta$ = average true effect size (i.e., without sampling or measurement error), $\\tau^2$ = variance of true effect sizes, $\\theta_i$ = study true effect size, $\\gamma_i$ = study effect size with sampling error $\\sigma_i^2$, $N_i$ = study sample size, $R_i$ = study reliability, $\\bar{R}$ = average reliability across studies, $\\delta$ = standard deviation of reliabilities across studies, $r_i$ = observed study effect size with sampling and measurement error, $\\bar{r}$ = average observed effect size across studies."
